\documentclass[11pt,openany]{memoir}

\setstocksize{22.8cm}{15.25cm}
\settrimmedsize{\stockheight}{\stockwidth}{*}
\setlrmarginsandblock{1.2cm}{0.8cm}{*} % Left and right margin
\setulmarginsandblock{2.5cm}{2.5cm}{*}  % Upper and lower margin
\checkandfixthelayout 

\usepackage{lettrine}
\usepackage{type1cm}

\renewcommand \thechapter{\Roman{chapter}}

\begin{document}

\title{The Metamorposis}
\author{Franz Kafka}
\date{}

\maketitle

\pagenumbering{arabic}


\chapter{}

\lettrine[lines=3]{O}{ne} morning, when Gregor Samsa woke from troubled dreams, he found
himself transformed in his bed into a horrible vermin.  He lay on
his armour-like back, and if he lifted his head a little he could
see his brown belly, slightly domed and divided by arches into stiff
sections.  The bedding was hardly able to cover it and seemed ready
to slide off any moment.  His many legs, pitifully thin compared
with the size of the rest of him, waved about helplessly as he
looked.

"What's happened to me?" he thought.  It wasn't a dream.  His room,
a proper human room although a little too small, lay peacefully
between its four familiar walls.  A collection of textile samples
lay spread out on the table - Samsa was a travelling salesman - and
above it there hung a picture that he had recently cut out of an
illustrated magazine and housed in a nice, gilded frame.  It showed
a lady fitted out with a fur hat and fur boa who sat upright,
raising a heavy fur muff that covered the whole of her lower arm
towards the viewer.

Gregor then turned to look out the window at the dull weather.
Drops of rain could be heard hitting the pane, which made him feel
quite sad.  "How about if I sleep a little bit longer and forget all
this nonsense", he thought, but that was something he was unable to
do because he was used to sleeping on his right, and in his present
state couldn't get into that position.  However hard he threw
himself onto his right, he always rolled back to where he was.  He
must have tried it a hundred times, shut his eyes so that he
wouldn't have to look at the floundering legs, and only stopped when
he began to feel a mild, dull pain there that he had never felt
before.

\chapter{}

\lettrine[lines=3]{I}{t} was not until it was getting dark that evening that Gregor awoke
from his deep and coma-like sleep.  He would have woken soon
afterwards anyway even if he hadn't been disturbed, as he had had
enough sleep and felt fully rested.  But he had the impression that
some hurried steps and the sound of the door leading into the front
room being carefully shut had woken him.  The light from the
electric street lamps shone palely here and there onto the ceiling
and tops of the furniture, but down below, where Gregor was, it was
dark.  He pushed himself over to the door, feeling his way clumsily
with his antennae - of which he was now beginning to learn the value
- in order to see what had been happening there.  The whole of his
left side seemed like one, painfully stretched scar,  and he limped
badly on his two rows of legs.  One of the legs had been badly
injured in the events of that morning - it was nearly a miracle that
only one of them had been - and dragged along lifelessly.

It was only when he had reached the door that he realised what it
actually was that had drawn him over to it; it was the smell of
something to eat.  By the door there was a dish filled with
sweetened milk with little pieces of white bread floating in it.  He
was so pleased he almost laughed, as he was even hungrier than he
had been that morning, and immediately dipped his head into the
milk, nearly covering his eyes with it.  But he soon drew his head
back again in disappointment; not only did the pain in his tender
left side make it difficult to eat the food - he was only able to
eat if his whole body worked together as a snuffling whole - but the
milk did not taste at all nice.  Milk like this was normally his
favourite drink, and his sister had certainly left it there for him
because of that, but he turned, almost against his own will, away
from the dish and crawled back into the centre of the room.

Through the crack in the door, Gregor could see that the gas had
been lit in the living room.  His father at this time would normally
be sat with his evening paper, reading it out in a loud voice to
Gregor's mother, and sometimes to his sister, but there was now not
a sound to be heard.  Gregor's sister would often write and tell him
about this reading, but maybe his father had lost the habit in
recent times.  It was so quiet all around too, even though there
must have been somebody in the flat.  "What a quiet life it is the
family lead", said Gregor to himself, and, gazing into the darkness,
felt a great pride that he was able to provide a life like that in
such a nice home for his sister and parents.  But what now, if all
this peace and wealth and comfort should come to a horrible and
frightening end? That was something that Gregor did not want to
think about too much, so he started to move about, crawling up and
down the room.

Once during that long evening, the door on one side of the room was
opened very slightly and hurriedly closed again; later on the door
on the other side did the same; it seemed that someone needed to
enter the room but thought better of it.  Gregor went and waited
immediately by the door, resolved either to bring the timorous
visitor into the room in some way or at least to find out who it
was; but the door was opened no more that night and Gregor waited in
vain.  The previous morning while the doors were locked everyone had
wanted to get in there to him, but now, now that he had opened up
one of the doors and the other had clearly been unlocked some time
during the day, no-one came, and the keys were in the other sides.

\chapter{}

\lettrine[lines=3]{N}{o-one} dared to remove the apple lodged in Gregor's flesh, so it
remained there as a visible reminder of his injury.  He had suffered
it there for more than a month, and his condition seemed serious
enough to remind even his father that Gregor, despite his current
sad and revolting form, was a family member who could not be treated
as an enemy.  On the contrary, as a family there was a duty to
swallow any revulsion for him and to be patient, just to be patient.

Because of his injuries, Gregor had lost much of his mobility -
probably permanently.  He had been reduced to the condition of an
ancient invalid and it took him long, long minutes to crawl across
his room - crawling over the ceiling was out of the question - but
this deterioration in his condition was fully (in his opinion) made
up for by the door to the living room being left open every evening.
 He got into the habit of closely watching it for one or two hours
before it was opened and then, lying in the darkness of his room
where he could not be seen from the living room, he could watch the
family in the light of the dinner table and listen to their
conversation - with everyone's permission, in a way, and thus quite
differently from before.

They no longer held the lively conversations of earlier times, of
course, the ones that Gregor always thought about with longing when
he was tired and getting into the damp bed in some small hotel room.
 All of them were usually very quiet nowadays.  Soon after dinner,
his father would go to sleep in his chair; his mother and sister
would urge each other to be quiet; his mother, bent deeply under the
lamp, would sew fancy underwear for a fashion shop; his sister, who
had taken a sales job, learned shorthand and French in the evenings
so that she might be able to get a better position later on.
Sometimes his father would wake up and say to Gregor's mother
"you're doing so much sewing again today!", as if he did not know
that he had been dozing - and then he would go back to sleep again
while mother and sister would exchange a tired grin.

With a kind of stubbornness, Gregor's father refused to take his
uniform off even at home; while his nightgown hung unused on its peg
Gregor's father would slumber where he was, fully dressed, as if
always ready to serve and expecting to hear the voice of his
superior even here.  The uniform had not been new to start with, but
as a result of this it slowly became even shabbier despite the
efforts of Gregor's mother and sister to look after it.  Gregor
would often spend the whole evening looking at all the stains on
this coat, with its gold buttons always kept polished and shiny,
while the old man in it would sleep, highly uncomfortable but
peaceful.


\end{document}
